\songti
\begin{center}
  \zihao{-2}\textbf{电力系统网源协调控制系统开发}
\end{center}
\vspace{0.5cm}\noindent\textbf{[摘要]\quad}
在如今的电力市场和大力发展新能源电力、大量分布式、小容量新能源机组需要并网的环境下，网源协调的问题日益突出。良好的网源协调能力对电力系统运行有着极大的作用。然而现有的网源协调分析和控制方法主要用于集中式、大容量机组，针对小容量、分布式并网主体（如风力发电、光伏发电等）的应用尚不成熟。本文根据《南方区域“两个细则”》以及《南方区域“两个细则”修订内容》，结合小容量、分布式并网主体自身的特点，提出了对应的考核制度，并为其提供一个通用性的考核平台框架。
通过该平台可以实时可视化分析并网主体的网源协调种指标，从改善电厂发电、调频调峰以及出力策略等方面为改善并网主体的网源协调动作提供优化方案，进一步改善该类机组的网源协调问题。

%系统等方面出发，可视化显示多种指标体系，
%
%构建以新能源为主体的新型电力系统是我国2030年前实现碳达峰、2060年前实现碳中和的关键。针对风光等新能源机组存在等效转动惯量很小、缺乏相关频率调节功能及电压调节能力有限等缺点危害系统安全稳定运行的难题，可考虑开展新型电力系统网源协调分析与控制研究。然而，现有的网源协调分析与控制方法主要用于集中式、大容量的机组，尚未有研究将该分析与控制方法直接应用于分布式、小容量的并网主体（如风电、光伏、虚拟电厂等）上。为此，本项目计划：研究适用于分布式小容量并网主体的网源协调分析方法、研究适用于分布式小容量并网主体的网源协调控制方法、以及建设适用于分布式小容量并网主体网源协调分析与控制的通用性平台。项目研究成果将构建并网主体网源协调问题的分析与控制理论并形成一个适用于分布式小容量并网主体网源协调分析与控制的通用性平台，通过该平台可实时分析各并网主体的网源协调动作情况、可设计控制器优化各并网主体的网源协调动作使其满足并网要求。
\par\vspace{1cm}\noindent\textbf{[关键词]\quad}
\textbf{电力系统；网源协调；两个细则；一次调频；新能源功率预测}
\newpage

%English Abstract
\begin{center}
  \zihao{-2}\textbf{Development of Power System Grid-Ssource Coordination Control System}
\end{center}
\vspace{0.5cm}\noindent\textbf{\bf{Abstract}\quad}
Today, in the environment of the electricity market and a large number of distributed small capacity new energy generator sets that needed to be connected to the grid, the problem of gird-source coordination is much more serious than ever before. The gird-source coordination plays a great role in the operation of the power systerm. However, the existing gird-source coordination analysis and control methods are mainly designed for centralized and high-capacity generator sets. The application for those smaller and diastrbuted sets, such as wind power and photovoltaics, is immature. According to \textit{the Two Rules of the Southern Region} and \textit{the Revised Contents of the Two Rules of the Southern Region}, and in consideration of the characteristics of these generator sets, this paper puts forward the corresponding assessment system and provides a universal platform framework. The system visually displays a variety of indexs in order to provide a suggestion to improve the coordinated development of the Grid and the Source. Therefore it might helps to the problem of gird-source coordination.
\par\vspace{1cm}\noindent\textbf{Keywords\quad}
\textbf{Electrical Power System; Grid-Source Coordination; the \textit{Two Rules}; the Primary Frequency Modulation; New Energy Power Forecast}

